Model

### 2019-10-16 stats/model.Rmd
new way of savinf predictions

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)

@@

devtools::install_github("https://github.com/mhtess/webppl-sample-writer")

@@

var header = "iteration,a,b,c,d,e,f,g,h"
var callback = webpplSampleWriter.streamQueryCSV("../saves/samples.csv", header);

Infer({model,
      samples: 2,
      burn: 1,
      verbose: T,
      lag: 1,
      verboseLag: 1,
      method: "incrementalMH",
      onlyMAP: true,
      callbacks: [callback]});
'
```

@@

```{r}
sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  packages = c("utils/webppl-sample-writer")
)

@@

model <- read_csv("../saves/samples.csv")

@@

```{r}
log_like <- model %>%
  filter(a == "log_like")%>%
  select(-f, -d)%>%
  rename(type = a, 
         model =b,
         parameter = c, 
         log_like = e)

>>>>

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)

@@

@@

var header = "iteration,a,b,c,d,e,f,g,h"

var randomNumberForFile = Math.round(uniform(0, 1000))

var callback = webpplSampleWriter.streamQueryCSV("../saves/model/samples"+randomNumberForFile+".csv", header);

Infer({model,
      samples: 100,
      burn: 100,
      verbose: T,
      lag: 1,
      verboseLag: 5000,
      method: "incrementalMH",
      onlyMAP: true,
      callbacks: [callback]});
'
```

@@

```{r}
sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  packages = c("utils/webppl-sample-writer")
)

@@

model <- bind_rows(
  read_csv("../saves/model/samples126.csv")%>%mutate(chain = 1),
  read_csv("../saves/model/samples551.csv")%>%mutate(chain = 2),
  read_csv("../saves/model/samples661.csv")%>%mutate(chain = 3),
  read_csv("../saves/model/samples950.csv")%>%mutate(chain = 4)
)

@@

```{r}
log_like <- model %>%
  filter(a == "log_like")%>%
  select(-f, -d, -g, -h)%>%
  rename(type = a, 
         model =b,
         parameter = c, 
         log_like = e)%>%
  mutate(log_like = as.numeric(log_like))
